### 2025-04-07 download-football-data.qmd
20250406 - fix calculation

recomputeVars <- c(
  "pacr", # passing_yards / passing_air_yards
  "racr", # receiving_yards / receiving_air_yards
  "fg_pct", # fg_made / fg_att
  "pat_pct" # pat_att / pat_made
)

@@

nfl_actualStats_career_player <- nfl_actualStats_seasonal_player %>% 
  group_by(player_id) %>% 
  summarise(
    across(all_of(weightedAverageVars_byGames), ~ weighted.mean(.x, w = games, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byAttempts), ~ weighted.mean(.x, w = attempts, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byTargets), ~ weighted.mean(.x, w = targets, na.rm = TRUE)),
    across(all_of(concatenateVars), ~ paste(.x[!is.na(.x)], collapse = ";")),
    across(all_of(sumVars), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop") %>% 
  mutate(
    pacr = passing_yards / passing_air_yards,
    racr = receiving_yards / receiving_air_yards,
    fg_pct = fg_made / fg_att,
    pat_pct = pat_att / pat_made
  )

@@

nfl_actualStats_career_player_inclPost <- nfl_actualStats_seasonal_player_inclPost %>% 
  group_by(player_id) %>% 
  summarise(
    across(all_of(weightedAverageVars_byGames), ~ weighted.mean(.x, w = games, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byAttempts), ~ weighted.mean(.x, w = attempts, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byTargets), ~ weighted.mean(.x, w = targets, na.rm = TRUE)),
    across(all_of(concatenateVars), ~ paste(.x[!is.na(.x)], collapse = ";")),
    across(all_of(sumVars), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop") %>% 
  mutate(
    pacr = passing_yards / passing_air_yards,
    racr = receiving_yards / receiving_air_yards,
    fg_pct = fg_made / fg_att,
    pat_pct = pat_att / pat_made
  )

>>>>

recomputeVars <- c(
  "pacr", # passing_yards / passing_air_yards
  "racr", # receiving_yards / receiving_air_yards
  "fg_pct", # fg_made / fg_att
  "pat_pct" # pat_made / pat_att
)

@@

nfl_actualStats_career_player <- nfl_actualStats_seasonal_player %>% 
  group_by(player_id) %>% 
  summarise(
    across(all_of(weightedAverageVars_byGames), ~ weighted.mean(.x, w = games, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byAttempts), ~ weighted.mean(.x, w = attempts, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byTargets), ~ weighted.mean(.x, w = targets, na.rm = TRUE)),
    across(all_of(concatenateVars), ~ paste(.x[!is.na(.x)], collapse = ";")),
    across(all_of(sumVars), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop") %>% 
  mutate(
    pacr = passing_yards / passing_air_yards,
    racr = receiving_yards / receiving_air_yards,
    fg_pct = fg_made / fg_att,
    pat_pct = pat_made / pat_att
  )

@@

nfl_actualStats_career_player_inclPost <- nfl_actualStats_seasonal_player_inclPost %>% 
  group_by(player_id) %>% 
  summarise(
    across(all_of(weightedAverageVars_byGames), ~ weighted.mean(.x, w = games, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byAttempts), ~ weighted.mean(.x, w = attempts, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byTargets), ~ weighted.mean(.x, w = targets, na.rm = TRUE)),
    across(all_of(concatenateVars), ~ paste(.x[!is.na(.x)], collapse = ";")),
    across(all_of(sumVars), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop") %>% 
  mutate(
    pacr = passing_yards / passing_air_yards,
    racr = receiving_yards / receiving_air_yards,
    fg_pct = fg_made / fg_att,
    pat_pct = pat_made / pat_att
  )
